systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-25 paper/trunk/systemfit_estimation.tex
added section about the code inside the systemfit package (this is suggested by the JSS)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@617 591db2bd-e0a0-4d22-8c19-2192dbb7da31
the capitalization of all (sub)(sub)section headers is now in sentence-style (according to the guidelines of the JSS)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@618 591db2bd-e0a0-4d22-8c19-2192dbb7da31
very small edits to improve readibility
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@630 591db2bd-e0a0-4d22-8c19-2192dbb7da31

When the disturbances are contemporaneously correlated, a Generalized 
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case the GLS is generally called °Seemingly Unrelated Regression°
(SUR) \citep{zellner62}.
Note, while an unbiased OLS or WLS estimation requires only that 
the regressors and the disturbance terms of each single 
equation are uncorrelated
$( E \left[ u_i | X_i \right] = 0 \; \forall \; i )$,
a consistent SUR estimation requires that all disturbance terms and all 
regressors are uncorrelated
$( E \left[ u | X \right] = 0 )$.

The SUR estimator can be obtained by:%
\footnote{
To calculate $\Omega^{-1}$ it is not necessary to invert 
the (huge) $\Omega$ matrix, 
because it is sufficient to invert the (small) $\Sigma$ matrix and
calculate it by $\Omega^{-1} = \Sigma^{-1} \otimes I$
\citep[p.\ 342]{greene03}.
}
\begin{equation}
   \widehat{\beta}_{SUR} = \left( X' \Omega^{-1} X \right)^{-1} X' \Omega^{-1} y
\end{equation}
with $\Omega = \Sigma \otimes I$ and
$\sigma_{ij} = E \left( u_i' u_j \right)$.
And the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov \left[ \widehat{\beta}_{SUR} \right] = \left( X' \Omega^{-1} X \right)^{-1}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Two-Stage least squares (2SLS)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Three-Stage least squares (3SLS)}

>>>>

When the disturbances are contemporaneously correlated, a Generalized 
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case, the GLS is generally called "Seemingly Unrelated Regression"
(SUR) \citep{zellner62}.
It should be noted that while an unbiased OLS or WLS estimation requires only that 
the regressors and the disturbance terms of each single 
equation are uncorrelated
$( E \left[ u_i | X_i \right] = 0 \; \forall \; i )$,
a consistent SUR estimation requires that all disturbance terms and all 
regressors are uncorrelated
$( E \left[ u | X \right] = 0 )$.

The SUR estimator can be obtained by:
\begin{equation}
   \widehat{\beta}_{SUR} = \left( X' \Omega^{-1} X \right)^{-1} X' \Omega^{-1} y
   \label{eq:sur}
\end{equation}
with $\Omega = \Sigma \otimes I$ and
$\sigma_{ij} = E \left( u_i' u_j \right)$.
And the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov \left[ \widehat{\beta}_{SUR} \right] = \left( X' \Omega^{-1} X \right)^{-1}
   \label{eq:surCov}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Two-stage least squares (2SLS)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Three-stage least squares (3SLS)}
